Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-08-21 R/SubGenome Analysis.Rmd
Added venn filtered by MF terms

---
title: 'Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating
  subgenome assignments in maize'
params:
  fileParser: ../Perl/parseKsKnFile.pl
  goDataFile: ../Data/GO from maizecyc.tab
  log10_ks_cutoff: 0
  synMapOutputFile: 6807_8082.CDS-CDS.lastz.tdd10.cs0.filtered.dag.all.go_D20_g10_A5.aligncoords.gcoords.ks
  # inputDataFile: ../Data/sorghum_v1_vs_maize_v1.tab
  # subGenomeFile: ../Data/outfile_processed_byHand.tab

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(readxl)
library(ggplot2)
library(tidyr)
library(dplyr)
library(VennDiagram)
library(gridExtra)
```

@@

```{r importSynMapData, include=FALSE}
source("~/git/SubGenomes/R/parseSubgenomes.R")
source("~/git/SubGenomes/R/addGOTerms.R")
source("~/git/SubGenomes/R/parseGOSlim.R")

@@

>>>>

---
title: 'Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating
  subgenome assignments in maize'
params:
  fileParser: ../Perl/parseKsKnFile.pl
  goDataFile: ../Data/GO from maizecyc.tab
  log10_ks_cutoff: 0
  # synMapOutputFile: 6807_8082.CDS-CDS.lastz.tdd10.cs0.filtered.dag.all.go_D20_g10_A5.aligncoords.gcoords.ks
  # inputDataFile: ../Data/sorghum_v1_vs_maize_v1.tab
  # subGenomeFile: ../Data/outfile_processed_byHand.tab

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(topGO)
library(readr)
library(readxl)
library(ggplot2)
library(tidyr)
library(dplyr)
library(VennDiagram)
library(gridExtra)
```

@@

```{r importSynMapData, include=FALSE}
source("~/git/SubGenomes/R/parseSubgenomes.R")
source("~/git/SubGenomes/R/addGOTerms.R")
source("~/git/SubGenomes/R/parseGOSlim.R")
# source("~/git/SubGenomes/R/createTopGO.R")

MFterms <- ls(GOMFTerm)

@@

GO Terms by subgenome, only counting GO Terms that are in GOSlimPlant and are Molecular Function terms.

```{r GOTerms_by_subgenome_goslim_MF, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4, fig.height=4}
# All EV-Codes, Unique GO Terms
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% select("GO Term") %>% 
    filter(`GO Term` %in% MFterms) %>% distinct() %>% nrow(),
  area2 = goAnnotations.sub2 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% select("GO Term") %>% 
    filter(`GO Term` %in% MFterms) %>% distinct() %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% select("GO Term") %>% filter(`GO Term` %in% MFterms), 
                         goAnnotations.sub2 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% select("GO Term") %>% filter(`GO Term` %in% MFterms)) %>%
                          nrow(), 
  category = c("SubGenome 1", "SubGenome 2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term by Subgenome\n(All EV-Codes, GOSlim, MF only)")

#EXP only, Unique GO Terms
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% filter(grepl("EV-EXP", EVCode)) %>% select("GO Term") %>% 
    filter(`GO Term` %in% MFterms) %>% distinct() %>% nrow(),
  area2 = goAnnotations.sub2 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% filter(grepl("EV-EXP", EVCode)) %>% select("GO Term") %>% 
    filter(`GO Term` %in% MFterms) %>% distinct() %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm"))%>% filter(grepl("EV-EXP", EVCode)) %>% select("GO Term") %>% 
                           filter(`GO Term` %in% MFterms), 
                         goAnnotations.sub2 %>% inner_join(goSlim, by=c("GO Term" = "GOSlimTerm")) %>% filter(grepl("EV-EXP", EVCode)) %>% select("GO Term") %>% 
                           filter(`GO Term` %in% MFterms)
                         ) %>% nrow(), 
  category = c("SubGenome 1", "SubGenome 2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term by Subgenome\n(EV-EXP, GOSlim, MF only)")
```
